### 2018-10-04 CO759-ExtendendFormulations/assignments/A1.tex
starting p4

>>>>

%Problem 4
\section{}
\paragraph{}
Let $P \subseteq \R^d$ be a full-dimensional polytope with $0_d$ in its interior.
\subsection*{Sufficiency}
\paragraph{}
Suppose that $Q\subseteq \R^n$ is a polyhedron with at most $f$ facets, and $p:\R^n \rightarrow \R^d$ is an affine map so that $(Q,p)$ defines an extension of $P$. We define the \emph{polar} of $P$ as follows
$$P^* := \{x \in \R^d : y^Tx \leq 1, \forall y \in P\}.$$
From the previous Problem we may assume that $Q$ is a polytope. Suppose that there is a matrix $A \in \R^{d\times n}$ and $b \in \R^d$ such that $p(x) = Ax + b$ for all $x \in Q$. We claim that we may assume $b = 0$. Since $P$ is full-dimensional, $A$ as full row rank $d$. Thus $A$ has right inverse $A^{-1}_R$. Let $Q_1 = Q + \{-A^{-1}_Rb\}$. Then for all $x \in Q$,
$A(x + A^{-1}_Rb) = Ax  + b  = p(x).$ So the linear map which sends $x$ to $Ax$ maps $Q_1$ to $P$. Since $Q_1$ is a translation of $Q$ it has the same number of facets as $Q$. Thus we may assume $p$ is a linear map, i.e. $b=0$.
\paragraph{}
Let $Q' = Q^*$ and let $\cL' = \text{rowspace}(A)$. We claim $P^*$ is linearly isomorphic to $Q' \cap \cL'$. Since $Q'$ is the polar dual of $Q$, the number of vertices of $Q'$ is equal to the number of facets of $Q$: $f$.
\subsection*{Necessity}
\paragraph{}
Suppose that $Q'\subseteq \R^{n'}$ is a polytope with at most $f$ vertices, and $\cL \subseteq R^{n'}$ is an affine space such that $P^*$ is linearly isomorphic to $Q' \cap \cL'$.
